The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Minor

\subsection{Progress in Solver Performance.}

@@

\subsection{Unique Solutions.}

@@

\subsection{Use of Parallelism.}

@@

It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results. For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018 and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.

>>>>

\subsection{Progress in Solver Performance}

@@

\subsection{Unique Solutions}

@@

\subsection{Use of Parallelism}

@@

It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results. For example, Alt-Ergo solves the most satisfiable problems in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable problems in QF\_LIA.
